\documentclass[12pt]{article}
\usepackage[paper=letterpaper,margin=2cm]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{newtxtext, newtxmath}
\usepackage{enumitem}
\usepackage{titling}
\usepackage[colorlinks=true]{hyperref}

\setlength{\droptitle}{-6em}

% Enter the specific assignment number and topic of that assignment below, and replace "Your Name" with your actual name.
\title{Assignment \#4}
\author{Aidan Traboulay}
\date{\today}

\begin{document}
\maketitle
\begin{enumerate}[leftmargin=\labelsep]
\item Suppose that a "word" is any string of seven letters of the alphabet, with repeated letters allowed.
    \begin{enumerate}
        \item How many words begin with A or B and end with A or B?
        \item How many words begin with a vowel or end with a vowel?
    \end{enumerate}

\item Consider all bit strings of length 12.
    \begin{enumerate}
        \item How many begin with 110?
        \item How many have exactly four 1’s?
    \end{enumerate}

\item A club with 20 women and 17 men needs to form a committee of size six.
    \begin{enumerate}
        \item How many committees are possible if the committee must have three women and three men?
        \item How many committees are possible if the committee must have at least two men?
    \end{enumerate}

\item Use the binomial theorem to expand $(2c - 3d)^4.$

\item 
    \begin{enumerate}
        \item What is the probability that a fair coin lands Heads 6 times in a row?
        \item What is the probability that a fair coin lands Heads 4 times out of 5 flips?
    \end{enumerate}

\item Suppose you pick two cards, one at a time, at random, from an ordinary deck of
52 cards. Find
    \begin{enumerate}
        \item $ p $ (both cards are diamonds).
        \item $ p $ (the cards form a pair).
    \end{enumerate}
    
\item Suppose you have 40 different books (20 math books, 15 history books, and 5
geography books).
    \begin{enumerate}
        \item You pick two books at random, one at a time. What is the probability that both books are history books?
        \item You pick two books at random, one at a time. What is the probability that the two books are from different disciplines?
    \end{enumerate}

\item Suppose you pick a bit string from the set of all bit strings of length ten.
    \begin{enumerate}
        \item What is the probability that the bit string has exactly two 1’s?
        \item What is the probability that the bit string has exactly two 1’s, given that the string begins with a 1?
    \end{enumerate}
\end{enumerate}
\end{document}
